High-Dim Project

### 2014-12-19 highdim-paper/paper.tex
added references bbl and bst to paper
added \ref to algorithm

Many choices are available for the regularizer $r$. In (ref ???), they use
the group lasso, where each row in $W$ is a group. The associated regularizer 
then is $r(W) = \lambda\sum_j^p \|W_{j:}\|_2$ where $\lambda$ is a parameter
that adjusts the strength of the regularization.
This has the effect of producing a few rows of non-zero values in $W$;
since each row corresponds to an individual feature, the optimal sparse $W^*$
yields a fast-evaluating decision function, i.e. most features are 
ignored at test time.

To minimize this multiclass classification group lasso objective, ??? use 
coordiante descent, iteratively solving a sub-problem with respect to a 
single group. Figure ? shows a general outline of algorithm that involves
computing the partial gradient with respect to the 
current group $j$, the prox
operator of the L2 norm, and a final line search to identify an appropriate
step size for the current update.

\begin{algorithm}
 \For{$i \gets 1, \ldots, max\;iters $}{
     \For{$j \gets 1, \ldots, p$}{
        Compute gradient $l^\prime(W)_{j:}$\\
        Choose $\mathcal{L}_j$\\
        Compute \\
        $\;\;\;\;V_j = W_{j:} - \frac{1}{\mathcal{L}_j}l^\prime(W)_{j:}$\\
        $\;\;\;\;W_{j:}^* 
          = \operatorname{Prox}_{\frac{\lambda}{\mathcal{L}_j}\|\cdot\|_j}
         (V_j)$\\

@@

\section{Conclusion}
% include your own bib file like this:
%\bibliographystyle{acl}
%\bibliography{acl2014}

%\begin{thebibliography}{}
%
%\bibitem[\protect\citename{Aho and Ullman}1972]{Aho:72}
%Alfred~V. Aho and Jeffrey~D. Ullman.
%\newblock 1972.
%\newblock {\em The Theory of Parsing, Translation and Compiling}, volume~1.
%\newblock Prentice-{Hall}, Englewood Cliffs, NJ.
%
%\bibitem[\protect\citename{{American Psychological Association}}1983]{APA:83}
%{American Psychological Association}.
%\newblock 1983.
%\newblock {\em Publications Manual}.
%\newblock American Psychological Association, Washington, DC.
%
%\bibitem[\protect\citename{{Association for Computing Machinery}}1983]{ACM:83}
%{Association for Computing Machinery}.
%\newblock 1983.
%\newblock {\em Computing Reviews}, 24(11):503--512.
%
%\bibitem[\protect\citename{Chandra \bgroup et al.\egroup }1981]{Chandra:81}
%Ashok~K. Chandra, Dexter~C. Kozen, and Larry~J. Stockmeyer.
%\newblock 1981.
%\newblock Alternation.
%\newblock {\em Journal of the Association for Computing Machinery},
%  28(1):114--133.
%
%\bibitem[\protect\citename{Gusfield}1997]{Gusfield:97}
%Dan Gusfield.
%\newblock 1997.
%\newblock {\em Algorithms on Strings, Trees and Sequences}.
%\newblock Cambridge University Press, Cambridge, UK.
%
%\end{thebibliography}

>>>>

Many choices are available for the regularizer $r$. \cite{blondel2013block} uses
the group lasso, where each row in $W$ is a group. The associated regularizer 
then is $r(W) = \lambda\sum_j^p \|W_{j:}\|_2$ where $\lambda$ is a parameter
that adjusts the strength of the regularization.
This has the effect of producing a few rows of non-zero values in $W$;
since each row corresponds to an individual feature, the optimal sparse $W^*$
yields a fast-evaluating decision function, i.e. most features are 
ignored at test time.

To minimize this multi-class classification group lasso objective, coordinate descent method could be used, which iteratively solve a sub-problem with respect to a 
single group. Algorithm~\ref{fig:cooddes} shows a general outline of algorithm that involves
computing the partial gradient with respect to the 
current group $j$, the prox
operator of the L2 norm, and a final line search to identify an appropriate
step size for the current update.

\begin{algorithm}
\caption{coordinate descent among groups}
\label{fig:cooddes}
 \For{$i \gets 1, \ldots, max\;iters $}{
     \For{$j \gets 1, \ldots, p$}{
        Compute gradient $l^\prime(W)_{j:}$\\
        Choose $\mathcal{L}_j$\\
        Compute \\
        $\;\;\;\;V_j = W_{j:} - \frac{1}{\mathcal{L}_j}l^\prime(W)_{j:}$\\
        $\;\;\;\;W_{j:}^* 
          = \operatorname{Prox}_{\frac{\lambda}{\mathcal{L}_j}\|\cdot\|_j}
         (V_j)$\\

@@

\section{Conclusion}
% include your own bib file like this:
\bibliographystyle{acl}
\bibliography{ref}
